---
title: "EEG Rhyme Behavioral Analysis"
author: "Julie M. Schneider"
date: '2022-08-11'
output: html_document
---
```{r}
# Run every time
library(dplyr)
library(tidyr)
library(readr)
library(tidyverse)
library(plyr)
library(rlang)
library(fs)
library(readxl)
library(data.table)
library(stringr)
library(readxl)
```
## Load individual event files
### NOTE: Be sure to open the .txt file, delete all header rows and save as a .csv
```{r}
file.list <- list.files(path="/Volumes/juschnei/lendlab/projects/EEG_Rhyme/analysis/txtdir",pattern="*_bins.csv", full.names = TRUE)

dt.list <- sapply(file.list, fread, simplify = FALSE, data.table = F)

df <- rbindlist(dt.list, idcol = 'filename')
df<-subset(df, select = c("filename","V1", "V3", "V5","V10"))
names(df)[1]<-"ID"
names(df)[2]<-"trial"
names(df)[3]<-"code"
names(df)[4]<-"time"
names(df)[5]<-"bin"

df$ID<-str_remove(df$ID,"/Volumes/juschnei/lendlab/projects/EEG_Rhyme/analysis/txtdir/eeg_rhyme_")
df$ID<-str_remove(df$ID, "_bins.csv")
df$ID<-as.numeric(df$ID)
```

## Compute whether individuals significantly differed in the number "learned" versus "not learned" during exposure
```{r}
## If bin contains 13,15,17 or 19 it was "learned" during exposure
patterns <- c("13", "15", "17","19")
learned <- filter(df, grepl(paste(patterns, collapse="|"), bin))
## If bin contains 14,16,18,20 it was "not learned" during exposure
patterns2 <- c("14", "16", "18","20")
notlearned <- filter(df, grepl(paste(patterns2, collapse="|"), bin))

## Count how many trials per person there are for learned versus not learned
learnedcount<-ddply(learned, .(ID), nrow)
notlearnedcount<-ddply(notlearned, .(ID), nrow)

t.test(learnedcount$V1,notlearnedcount$V1, paired = TRUE)
```

## Post-testAnalysis
### Need to load answer sheet and compare to post-test (need to also load in their order)
```{r}
EEG_orders <- read_excel("/Volumes/juschnei/lendlab/projects/EEG_Rhyme/participant_database.xlsx", sheet = "EEG")
PTans<-read.csv("post_test_answers.csv", header = TRUE)

names(EEG_orders)[1]<-"ID"
EEG_orders$ID<-str_remove(EEG_orders$ID, "eeg_rhyme_")
EEG_orders$ID<-as.numeric(EEG_orders$ID)

EEG_orders<-EEG_orders[, c(1,8,9)]
PT_scoring<-merge(EEG_orders,df, by = "ID")
PT_scoring$count<-1:nrow(PT_scoring)
```

## Post test 1 Scoring
### Identify and extract trials with response; evaluate overall accuracy
```{r}
GetIDsAfter = function(x) {
  v =(x+1)
}

PT_scoring %>%                        # from your dataset
  filter(code == 31|code == 30) %>%            # keep rows where b > 1
  pull(count) %>%                  # get the positions
  map(GetIDsAfter) %>%      # for each position apply the function
  unlist() %>%                 # unlist all sets indices
  unique() -> ids_to_remain    # keep unique ones and save them in a vector

#PT_scoring$backup = PT_scoring$code                  # copy column c as d
PT_scoring$code[-ids_to_remain] = NA     # put NA to all positions not in our vector

PT_scoring$code <- as.numeric(as.character(PT_scoring$code))
PT_one<-PT_scoring %>% drop_na(code)

## Important! Check that each person has 15 trials
count(PT_one, "ID")
PT_one$count<-ave(PT_one$ID, PT_one$ID, FUN=seq_along)

PTans_one<-PTans %>% filter(Post_test == "1")
PTans_one$count<-ave(PTans_one$Order, PTans_one$Order, FUN=seq_along)

PT_one<-left_join(PT_one, PTans_one, by=c("Order","count"))

PT_one$accuracy <- ifelse(PT_one$code == PT_one$Correct_response, 1, 0)
PT_one %>%
  group_by(ID) %>%
  summarise_at(vars(accuracy), list(name = mean))
```
## Post test 2 Scoring
```{r}
PT_scoring<-merge(EEG_orders,df, by = "ID")
PT_scoring$count<-1:nrow(PT_scoring)

GetIDsAfter = function(x) {
  v =(x+1)
}

PT_scoring %>%                        # from your dataset
  filter(code == 213|code == 214) %>%            # keep rows where b > 1
  pull(count) %>%                  # get the positions
  map(GetIDsAfter) %>%      # for each position apply the function
  unlist() %>%                 # unlist all sets indices
  unique() -> ids_to_remain    # keep unique ones and save them in a vector

#PT_scoring$backup = PT_scoring$code                  # copy column c as d
PT_scoring$code[-ids_to_remain] = NA     # put NA to all positions not in our vector

PT_scoring$code <- as.numeric(as.character(PT_scoring$code))
PT_two<-PT_scoring %>% drop_na(code)

## Important! Check that each person has 15 trials
count(PT_two, "ID")
PT_two$count<-ave(PT_two$ID, PT_two$ID, FUN=seq_along)

PTans_two<-PTans %>% filter(Post_test == "2")
PTans_two$count<-ave(PTans_two$Order, PTans_two$Order, FUN=seq_along)

PT_two<-left_join(PT_two, PTans_two, by=c("Order","count"))

PT_two$accuracy <- ifelse(PT_two$code == PT_two$Correct_response, 1, 0)
PT_two %>%
  group_by(ID) %>%
  summarise_at(vars(accuracy), list(name = mean))
```

